Measuring individual differences in the understanding of gaze cues

### 2022-05-05 paper/manuscript.Rmd
starting the intro...

# Introduction 
Idea for an opener :)

Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences. For example ...

- why is social cognition important
- what methods are currently been used?: wellman
- what are common issues? 
- what to aim at. individual differences in developmental psychology
- what characteristics should a new task fulfill? reliable tasks, variation needed, more trials
- goal of the current project: standardized, easy to use continuous methods

"Recently, it was suggested that a range of cognitive tasks may reliably measure group differences but not individual differences (Hedge et al., 2018). As cognitive tests are commonly used to make inferences about individuals, it seems a worthwhile pursuit to improve the reliability with which individual differences are assessed using these tests. To judge the success of such pursuits, accurate estimates of reliability are required." (Pronk, Molenaar, Wiers and Murre, 2021, p. 1)
"Firstly, reliability is not only a function of task and population sample but also of scoring algorithms." (Pronk, Molenaar, Wiers and Murre, 2021, p. 9)
"Hence, we conclude that for the datasets included in our reanalysis, cognitive tasks may well have been able to measure individual differences, but that these differences may be relatively unstable over time (Kopp et al., 2021). In practice, this may make cognitive tasks suitable for cross-sectional research of individual differences, but not for longitudinal research." (Pronk, Molenaar, Wiers and Murre, 2021, p. 10)

@@

# Task design
- face value of task (or maybe in intro already?)

@@

Second, we assessed the test-retest reliability. We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients. Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [@rouder2019psychometrics]. We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`). For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function. The model computes a correlation between the participant specific estimates for each test day. This can be interpreted as the test-retest reliability. By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information. Most importantly, the model allows us to get an age-independent estimate for reliability. This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences [m: das noch bisschen konkreter machen. also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum].

>>>>

# Introduction 
Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.

## Why is social cognition important?

For example, a booming research area of comparative and developmental psychologists and philosophers has been *Social Cognition* and *Theory of Mind*. Although definitions vary, these umbrella terms are commonly used to describe the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences (TODO: cite). 
Children spend a large amount of time interacting with and learning from others in social contexts. A main research interest has, therefore, been when social-cognitive abilities emerge in children. Here, studies often tracked change on a group level and assessed at which average age children succeed in a task that relies on a given social-cognitive ability.

## What methods are currently been used? What are common issues?
In recent years, there has been a focus on replicability issues. These are especially prominent in developmental psychology since recruiting children and keeping them attentive and in a good mood requires a lot of effort and time. Often, this leads to small sample sizes or low numbers of trials per subject. Experimental paradigms often focus on dichotomous outcome variables and, therefore, high chance levels. 
In short, tasks were simply not designed to measure children’s abilities on an individual level. 
This has profound implications on what these studies can show: poor reliability of measures on an individual level may conceal relations between different aspects of cognition and also obscure developmental change. We argue that a systematic individual differences perspective on social-cognitive development is needed.

## An individual difference perspective

However, if we are interested in the co-development of social-cognitive abilities and a child’s pace of mastering developmental milestones, we need to focus on individual differences in social cognition. 
To study individual differences, variability in task performance needs to be reliable (i.e., systematically order individuals in the same way) and meaningful (i.e., differences in test scores correspond to differences in ability).

Few studies using traditional measures (e.g., false belief change-of-location tasks) address these issues. A recent paper by @hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies. The authors could show that this often does not emerge due to high measurement variance but rather low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences. 
In a similar vein, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a certain cognitive test is suited to draw inferences about individuals.

## Aim of the current project
We want to make individual differences measurable, in a systematic and reliable way. One of our main goals is, therefore, to create a task that induces variation between children. 
For getting precise person specific estimates, we need an accurate measure of a child's given underlying social-cognitive ability. To approach this issue, we focus on a continuous measure and short trials that facilitate more than a dozen replicates per subject. 
To estimate the effect of inter-individual differences, we need a large sample size since since some of the effects that we are looking for might be small. A standardized, easily accessible test procedure helps us to enable data collection at scale. 
Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's surrounding.

---

- why is social cognition important
- what methods are currently been used?: wellman
- what are common issues? 
- what to aim at. individual differences in developmental psychology
- what characteristics should a new task fulfill? reliable tasks, variation needed, more trials
- goal of the current project: standardized, easy to use continuous methods
- soc cog, gaze cue understanding small def (longer one dev paper)

@@

# Task design

@@

Second, we assessed the test-retest reliability. We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients. Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [@rouder2019psychometrics]. We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`). For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function. The model computes a correlation between the participant specific estimates for each test day. This can be interpreted as the test-retest reliability. By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information. Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person specific estimates. Most importantly, the model includes age as a fixed effect. The correlation between the two person specific estimates is consequently the age-independent estimate for test-retest reliability. This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences. A high correlation between our participant specific model estimates would speak for a high association between test days.
